### 2014-10-01 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add references for fuel packages

To estimate the type of fuel, fire size, and structure ventilation, on-scene photographs and post-incident reports were used. Based on these sources of information, the FDS model includes three source fires: 1) an initial couch fire in the basement, 2) a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the exterior basement balcony. The basement primarily contained upholstered polyurethane furniture fuel items, and the balcony was constructed of wood. The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.

@@

\item The secondary fuel packages in the basement were divided among four additional furniture items (two couches, a lounge, and a chair). The two large couches in the middle of the basement were specified with a peak HRR of 5~MW for each item. The lounge and chair located at the perimeter of the basement were specified with a peak HRR of 2~MW for each item. Therefore, the peak HRR of all four furniture items was a total of 14~MW.

>>>>

To estimate the type of fuel, fire size, and structure ventilation, on-scene photographs and post-incident reports were used. Based on these sources of information, the FDS model includes three source fires: 1) an initial couch fire in the basement, 2) a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the exterior basement balcony.

The basement primarily contained upholstered polyurethane furniture fuel items, and the balcony was constructed of wood. The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item. The HRRs of the additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1}. Other combustible items and furnishings such as tables, stools, bookshelves, and carpet were present in the basement living room. However, to simplify the analysis and specification of the design fire, only the above fuel items were included because they were considered to have contributed the largest amount of energy in this fire scenario.

@@

\item The secondary fuel packages in the basement were divided among four additional furniture items (two couches, a lounge, and a chair). The HRRs of these additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items, which reported HRRs of upholstered chairs and couches ranging from 2~MW to 5~MW~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1,Janssens:2012}. The two large couches in the middle of the basement were specified with a peak HRR of 5~MW for each item. The lounge and chair located at the perimeter of the basement were specified with a peak HRR of 2~MW for each item. Therefore, the peak HRR of all four furniture items was a total of 14~MW.
